---
title: "Adstock Regression Analysis"
author: "Dhiren"
date: "31 July 2020"
output: word_document
---
```{r}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)    #creative graphics
#library(devtools)   #development tool
#library(dplyr)      #data manipulation
library(cowplot)    #ready theme for ggplot
library(gridExtra)  #Title and/or annotation
library(grid)       #Grid Graphic package
library(gtools)     #assit in develop,maintain and update packages
library(plyr)       #control over input output formats
library(reshape2)   #reshaping data prior to analysis
library(scales)     #gradient
library(raster)     #for raster plot
library(rasterVis)  #raster using ggplot
library(rgdal)      #Geospatical data abstraction
library(RColorBrewer)#Sensible color schemes
library(gplots)     #tool for plotting
library(sm)         #for calculating density for each dataset
library(tseries)    #for Jarque-Bera Test and Kolmogorov Smirnov Test
library(readxl)
library(openxlsx)
library(corrplot)
library(corrgram)
library(ISLR)
library(boot)
library(DAAG)
options(warn=-1)
options(max.print=1000000)
```

```{r}
set.seed(4321)
getwd()
setwd("C:/Users/Dhiru/Desktop/data science")
getwd()

dataset <- read_excel("data2.xlsx")
class(dataset)
nrow(dataset)
#37-2=35
ncol(dataset)
#13
attach(dataset)


#Removing one header and renaming each column


names(dataset) <- as.matrix(dataset[1, ])
dataset <- dataset[-1, ]
dataset[] <- lapply(dataset, function(x) type.convert(as.character(x)))
View(dataset)
nrow(dataset)
#36

str(dataset)
summary(dataset)


#for(i in 1:nrow(dataset)){
# date<- as.Date(as.numeric(dataset[i,1]), origin = "1899-12-30")
#}
#dataset$Month <-date
#as.Date(42705, origin = "1899-12-30")
#as.Date(as.numeric(dataset[1,1]), origin = "1899-12-30")

#changing date format from excel to R
for(i in 1:nrow(dataset)){
  dataset[i,1] = toString(openxlsx::convertToDate(dataset[i,1]))
  }



View(dataset)
#reversing data set datewise

dataset <- dataset[36:1,]
str(dataset)

sapply(dataset[2],sd)
sapply(dataset[3],sd)
sapply(dataset[4],sd)
sapply(dataset[5],sd)
sapply(dataset[6],sd)
sapply(dataset[7],sd)
sapply(dataset[8],sd)
sapply(dataset[9],sd)
sapply(dataset[10],sd)
sapply(dataset[11],sd)
sapply(dataset[12],sd)
sapply(dataset[13],sd)


par(mfrow=c(2,2))

boxplot(dataset[,2:5],names = c("Magazine","Newspaper","Radio","OOH"),col = "blue")

boxplot(dataset[,6:9],names = c("TV","Search","Display","Social"),col = "blue")

boxplot(dataset[,10:12],names = c("Price1","Price2","Price3"),col = "blue")

boxplot(dataset[,13],names = c("Sales"),col = "blue",xlab="Sales")


#str(dataset$Month)
par(mfrow=c(2,2))
#dataset[1,1]

magazine<-ts(dataset[,2],frequency = 12, start = c(2016,4)) 
#plot.ts(magazine,col='red',xlab = "Year, Month")

newspaper<-ts(dataset[,3],frequency = 12, start = c(2016,4))
#plot(newspaper,col='red',xlab = "Year, Month")

radio<-ts(dataset[,4],frequency = 12, start = c(2016,4))
#plot(radio,col='red',xlab = "Year, Month")

ooh<-ts(dataset[,5],frequency = 12, start = c(2016,4))
#plot(ooh,col='red',xlab = "Year, Month")

par(mfrow=c(2,2))

tv<-ts(dataset[,6],frequency = 12, start = c(2016,4))
#plot(tv,col='red',xlab = "Year, Month")

search<-ts(dataset[,7],frequency = 12, start = c(2016,4))
#plot(search,col='red',xlab = "Year, Month")

display<-ts(dataset[,8],frequency = 12, start = c(2016,4))
#plot(display,col='red',xlab = "Year, Month")

social<-ts(dataset[,9],frequency = 12, start = c(2016,4))
#plot(social,col='red',xlab = "Year, Month")

par(mfrow=c(1,1))
sales<-ts(dataset[,13],frequency = 12, start = c(2016,4))
#plot(sales,col='blue',xlab = "Year, Month")
```
timeseries<-cbind(magazine,newspaper)
timeseries<-cbind(timeseries,radio)
timeseries<-cbind(timeseries,ooh)
timeseries<-cbind(timeseries,tv)
timeseries<-cbind(timeseries,search)
timeseries<-cbind(timeseries,display)
timeseries<-cbind(timeseries,social)
timeseries1<-cbind(timeseries,dataset$Month)
colnames(timeseries)<-c('magazine','newspaper','radio','ooh','tv','search','display','social')
View(timeseries1)
colnames(timeseries1)<-c('magazine','newspaper','radio','ooh','tv','search','display','social','month')
#ts.plot(timeseries1[1])
```{r}
dataset <- as.data.frame(dataset)



corrgram(dataset,main="Adstock Data",lower.panel=panel.pts, upper.panel=panel.conf,
         diag.panel=panel.density)

corrgram(dataset,main="Adstock Data", upper.panel=panel.cor)




dataset2<-dataset[complete.cases(dataset),]

```


```{r}
par(mfrow=c(2,2))
  rmax <- 0
	corrmax <- -1
	rates <- seq(0.00, 1.00, by = 0.01)
	corrs <- vector()
	adstock <- stats::filter(dataset2[,2], filter=r, method = "recursive")
  #cor(adstock,dataset2[,13])
	for(r in rates){
		adstock <- stats::filter(dataset2[,2], filter=r, method = "recursive")
		corr <- cor(adstock,dataset2[,13])
		if(corr>corrmax){
			corrmax <- corr
			rmax <- r
		}
		corrs <- append(corrs, corr)
	}
	
	plot(rates,corrs,xlab="rates",ylab="Magazine")
	rmax
	#magazine rate 0.04
	
	rmax <- 0
	corrmax <- -1
	rates <- seq(0.00, 1.00, by = 0.01)
	corrs <- vector()
	adstock <- stats::filter(dataset2[,3], filter=r, method = "recursive")
  #cor(adstock,dataset2[,13])
	for(r in rates){
		adstock <- stats::filter(dataset2[,3], filter=r, method = "recursive")
		corr <- cor(adstock,dataset2[,13])
		if(corr>corrmax){
			corrmax <- corr
			rmax <- r
		}
		corrs <- append(corrs, corr)
	}
	
	plot(rates,corrs,xlab="rates",ylab="Newspaper")
	rmax
	# newspaper rate 0
	
	rmax <- 0
	corrmax <- -1
	rates <- seq(0.00, 1.00, by = 0.01)
	corrs <- vector()
	adstock <- stats::filter(dataset2[,4], filter=r, method = "recursive")
  #cor(adstock,dataset2[,13])
	for(r in rates){
		adstock <- stats::filter(dataset2[,4], filter=r, method = "recursive")
		corr <- cor(adstock,dataset2[,13])
		if(corr>corrmax){
			corrmax <- corr
			rmax <- r
		}
		corrs <- append(corrs, corr)
	}
	
	plot(rates,corrs,xlab="rates",ylab="Radio")
	rmax
	# radio rate 0

	rmax <- 0
	corrmax <- -1
	rates <- seq(0.00, 1.00, by = 0.01)
	corrs <- vector()
	adstock <- stats::filter(dataset2[,5], filter=r, method = "recursive")
  #cor(adstock,dataset2[,13])
	for(r in rates){
		adstock <- stats::filter(dataset2[,5], filter=r, method = "recursive")
		corr <- cor(adstock,dataset2[,13])
		if(corr>corrmax){
			corrmax <- corr
			rmax <- r
		}
		corrs <- append(corrs, corr)
	}
	
	plot(rates,corrs,xlab="rates",ylab="OOH")
	rmax
	# ooh rate 0
	
	rmax <- 0
	corrmax <- -1
	rates <- seq(0.00, 1.00, by = 0.01)
	corrs <- vector()
	adstock <- stats::filter(dataset2[,6], filter=r, method = "recursive")
  #cor(adstock,dataset2[,13])
	for(r in rates){
		adstock <- stats::filter(dataset2[,6], filter=r, method = "recursive")
		corr <- cor(adstock,dataset2[,13])
		if(corr>corrmax){
			corrmax <- corr
			rmax <- r
		}
		corrs <- append(corrs, corr)
	}
	
	plot(rates,corrs,xlab="rates",ylab="TV")
	rmax
	# tv rate 0
	
	rmax <- 0
	corrmax <- -1
	rates <- seq(0.00, 1.00, by = 0.01)
	corrs <- vector()
	adstock <- stats::filter(dataset2[,7], filter=r, method = "recursive")
  #cor(adstock,dataset2[,13])
	for(r in rates){
		adstock <- stats::filter(dataset2[,7], filter=r, method = "recursive")
		corr <- cor(adstock,dataset2[,13])
		if(corr>corrmax){
			corrmax <- corr
			rmax <- r
		}
		corrs <- append(corrs, corr)
	}
	
	plot(rates,corrs,xlab="rates",ylab="Search")
	rmax
	# search rate 1
	
	rmax <- 0
	corrmax <- -1
	rates <- seq(0.00, 1.00, by = 0.01)
	corrs <- vector()
	adstock <- stats::filter(dataset2[,8], filter=r, method = "recursive")
  #cor(adstock,dataset2[,13])
	for(r in rates){
		adstock <- stats::filter(dataset2[,8], filter=r, method = "recursive")
		corr <- cor(adstock,dataset2[,13])
		if(corr>corrmax){
			corrmax <- corr
			rmax <- r
		}
		corrs <- append(corrs, corr)
	}
	
	plot(rates,corrs,xlab="rates",ylab="Display")
	rmax
	# display rate 0
	
	rmax <- 0
	corrmax <- -1
	rates <- seq(0.00, 1.00, by = 0.01)
	corrs <- vector()
	adstock <- stats::filter(dataset2[,9], filter=r, method = "recursive")
  #cor(adstock,dataset2[,13])
	for(r in rates){
		adstock <- stats::filter(dataset2[,9], filter=r, method = "recursive")
		corr <- cor(adstock,dataset2[,13])
		if(corr>corrmax){
			corrmax <- corr
			rmax <- r
		}
		corrs <- append(corrs, corr)
	}
	
	plot(rates,corrs,xlab="rates",ylab="Social")
	rmax
	# social rate 0

	
adstock_rate <- 0.04
max_memory   <- 2
learn_rates <- rep(adstock_rate, max_memory+1) ^ c(0:max_memory)

ad1.adstock <- as.numeric(stats::filter(c(rep(0, max_memory), dataset2[,2]), learn_rates, method="convolution"))
#ad1.adstock <- function(x=dataset2[,2], rate=0.04){return(as.numeric(stats::filter(x=x, filter=rate, method="recursive")))}
ad1.adstock <- ad1.adstock[!is.na(ad1.adstock)]
# Graph Data
plot(seq(1,length(dataset2[,2])), dataset2[,2], type="h", 
     xlab="Time (in months)", ylab="Magazine", 
     ylim=c(0, max(c(dataset2[,2], ad1.adstock))), 
     frame.plot=FALSE)
lines(ad1.adstock)

adstock_rate <- 0
ad2.adstock <- as.numeric(stats::filter(c(rep(0, max_memory), dataset2[,3]), learn_rates, method="convolution"))
ad2.adstock <- ad2.adstock[!is.na(ad2.adstock)]
# Graph Data
plot(seq(1,length(dataset2[,3])), dataset2[,3], type="h", 
     xlab="Time (in months)", ylab="Newspaper", 
     ylim=c(0, max(c(dataset2[,3], ad2.adstock))), 
     frame.plot=FALSE)
lines(ad2.adstock)

adstock_rate <- 0
ad3.adstock <- as.numeric(stats::filter(c(rep(0, max_memory), dataset2[,4]), learn_rates, method="convolution"))
ad3.adstock <- ad3.adstock[!is.na(ad3.adstock)]
# Graph Data
plot(seq(1,length(dataset2[,4])), dataset2[,4], type="h", 
     xlab="Time (in months)", ylab="Radio", 
     ylim=c(0, max(c(dataset2[,4], ad3.adstock))), 
     frame.plot=FALSE)
lines(ad3.adstock)

adstock_rate <- 0
ad4.adstock <- as.numeric(stats::filter(c(rep(0, max_memory), dataset2[,5]), learn_rates, method="convolution"))
ad4.adstock <- ad4.adstock[!is.na(ad4.adstock)]
# Graph Data
plot(seq(1,length(dataset2[,5])), dataset2[,5], type="h", 
     xlab="Time (in months)", ylab="OOH", 
     ylim=c(0, max(c(dataset2[,5], ad4.adstock))), 
     frame.plot=FALSE)
lines(ad4.adstock)


adstock_rate <- 0
ad5.adstock <- as.numeric(stats::filter(c(rep(0, max_memory), dataset2[,6]), learn_rates, method="convolution"))
ad5.adstock <- ad5.adstock[!is.na(ad5.adstock)]
# Graph Data
plot(seq(1,length(dataset2[,6])), dataset2[,6], type="h", 
     xlab="Time (in months)", ylab="TV", 
     ylim=c(0, max(c(dataset2[,6], ad5.adstock))), 
     frame.plot=FALSE)
lines(ad5.adstock)


adstock_rate <- 1
ad6.adstock <- as.numeric(stats::filter(c(rep(0, max_memory), dataset2[,7]), learn_rates, method="convolution"))
ad6.adstock <- ad6.adstock[!is.na(ad6.adstock)]
# Graph Data
plot(seq(1,length(dataset2[,7])), dataset2[,7], type="h", 
     xlab="Time (in months)", ylab="Search", 
     ylim=c(0, max(c(dataset2[,7], ad6.adstock))), 
     frame.plot=FALSE)
lines(ad6.adstock)


adstock_rate <- 0
ad7.adstock <- as.numeric(stats::filter(c(rep(0, max_memory), dataset2[,8]), learn_rates, method="convolution"))
ad7.adstock <- ad7.adstock[!is.na(ad7.adstock)]
# Graph Data
plot(seq(1,length(dataset2[,8])), dataset2[,8], type="h", 
     xlab="Time (in months)", ylab="Display", 
     ylim=c(0, max(c(dataset2[,8], ad7.adstock))), 
     frame.plot=FALSE)
lines(ad7.adstock)


adstock_rate <- 0
ad8.adstock <- as.numeric(stats::filter(c(rep(0, max_memory), dataset2[,9]), learn_rates, method="convolution"))
ad8.adstock <- ad8.adstock[!is.na(ad8.adstock)]
# Graph Data
plot(seq(1,length(dataset2[,9])), dataset2[,9], type="h", 
     xlab="Time (in months)", ylab="Social", 
     ylim=c(0, max(c(dataset2[,9], ad8.adstock))), 
     frame.plot=FALSE)
lines(ad8.adstock)






nrow(dataset2)
#trend = nrow(dataset2)
trend = 1:35
View(dataset2)



modFit.3 <- glm(dataset2[,13]~trend+ad1.adstock+ad2.adstock+ad3.adstock+ad4.adstock+ad5.adstock+ad6.adstock+ad7.adstock+ad8.adstock+dataset2$Price1 + dataset2$Price2 + dataset2$Price3)

summary(modFit.3)
plot(modFit.3)

anova(modFit.3)

#mse_loocv <- cv.glm(dataset2,modFit.3)$delta[1]
mse_loocv <- cv.glm(dataset2,modFit.3,K=2)$delta[1]

mse_loocv

summary(mse_loocv)

par(mfrow=c(1,1))
# Graph Data
plot(seq(1,length(dataset2[,13])), dataset2[,13], type="h", 
     xlab="Time (in months)", ylab="Sales", 
     ylim=c(0, max(c(dataset2[,13], modFit.3$fitted.values))), 
     frame.plot=FALSE)
lines(modFit.3$y)
lines(modFit.3$fitted.values,col='red')
legend("topright", inset=0, title="Sales Predicted",
   c("Predicted"), fill="red", horiz=TRUE,box.lty=0)
	
```

```{r}

#sales return on ad spend 

Roas = dataset2$Sales / (magazine + newspaper + radio + ooh + tv + search + display + social)

Roas_pred = modFit.3$fitted.values / (magazine + newspaper + radio + ooh + tv + search + display + social)

summary(Roas)

summary(Roas_pred)

par(mfrow=c(1,2))
boxplot(Roas,names = c("Roas"),col = "blue",xlab = "Roas")
boxplot(Roas_pred,names = c("Roas_pred"),col = "red", xlab = 'Roas_pred')
par(mfrow=c(1,1))



seqplot.ts(Roas,Roas_pred, colx = 'black', coly = 'red',typex='l',typey='l',xlab='Time in month',ylab = 'Roas vs Roas_pred',main='Roas comparison')


```


#Calculating rate of Adstock
model_magazine<- arima(magazine,order=c(1,0,0))
model_magazine$coef
#0.7670794

model_newspaper<- arima(newspaper,order=c(1,0,0))
model_newspaper$coef
#1.159188e-02

model_radio<- arima(radio,order=c(1,0,0))
model_radio$coef
#7.842217e-01

model_ooh<- arima(ooh,order=c(1,0,0))
model_ooh$coef
#5.012274e-02

model_tv<- arima(tv,order=c(1,0,0))
model_tv$coef
# 0.5812592

model_search<- arima(search,order=c(1,0,0))
model_search$coef
#1.699707e-02

model_display<- arima(display,order=c(1,0,0))
model_display$coef
#1.410361e-01

model_social<- arima(social,order=c(1,0,0))
model_social$coef
#6.057506e-01

ad1.adstock <- function(x=dataset2[,2], rate=0.76){return(as.numeric(stats::filter(x=x, filter=rate, method="recursive")))}
ad2.adstock <- function(x=dataset2[,3], rate=0.011){return(as.numeric(stats::filter(x=x, filter=rate, method="recursive")))}
ad3.adstock <- function(x=dataset2[,4], rate=0.78){return(as.numeric(stats::filter(x=x, filter=rate, method="recursive")))}
ad4.adstock <- function(x=dataset2[,5], rate=0.05){return(as.numeric(stats::filter(x=x, filter=rate, method="recursive")))}
ad5.adstock <- function(x=dataset2[,6], rate=0.58){return(as.numeric(stats::filter(x=x, filter=rate, method="recursive")))}
ad6.adstock <- function(x=dataset2[,7], rate=0.017){return(as.numeric(stats::filter(x=x, filter=rate, method="recursive")))}
ad7.adstock <- function(x=dataset2[,8], rate=0.14){return(as.numeric(stats::filter(x=x, filter=rate, method="recursive")))}
ad8.adstock <- function(x=dataset2[,9], rate=0.61){return(as.numeric(stats::filter(x=x, filter=rate, method="recursive")))}




nrow(dataset2)
#trend = nrow(dataset2)
trend = 1:35
View(dataset2)

modFit.3 <- cv.lm(data=dataset2,form.lm = formula( dataset2[,13]~trend+ad1.adstock()+ad2.adstock()+ad3.adstock()+ad4.adstock()+ad5.adstock()+ad6.adstock()+ad7.adstock()+ad8.adstock()+dataset2$Price1 + dataset2$Price2 + dataset2$Price3),m=1, dots = FALSE, seed=29,plotit=T)

modFit.3 <- glm(dataset2[,13]~trend+ad1.adstock()+ad2.adstock()+ad3.adstock()+ad4.adstock()+ad5.adstock()+ad6.adstock()+ad7.adstock()+ad8.adstock()+dataset2$Price1 + dataset2$Price2 + dataset2$Price3)

summary(modFit.3)
plot(modFit.3)

anova(modFit.3)

mse_loocv <- cv.glm(dataset2,modFit.3)$delta[1]


mse_loocv

summary(mse_loocv)






dataset2[2]<-scale(dataset2[2])
dataset2[3]<-scale(dataset2[3])
dataset2[4]<-scale(dataset2[4])
dataset2[5]<-scale(dataset2[5])
dataset2[6]<-scale(dataset2[6])
dataset2[7]<-scale(dataset2[7])
dataset2[8]<-scale(dataset2[8])
dataset2[9]<-scale(dataset2[9])
dataset2[10]<-scale(dataset2[10])
dataset2[11]<-scale(dataset2[11])
dataset2[12]<-scale(dataset2[12])
dataset2[13]<-scale(dataset2[13])


magazine<-ts(dataset2[,2],frequency = 12, start = c(2016,4)) 
#plot.ts(magazine,col='red',xlab = "Year, Month")

newspaper<-ts(dataset2[,3],frequency = 12, start = c(2016,4))
#plot(newspaper,col='red',xlab = "Year, Month")

radio<-ts(dataset2[,4],frequency = 12, start = c(2016,4))
#plot(radio,col='red',xlab = "Year, Month")

ooh<-ts(dataset2[,5],frequency = 12, start = c(2016,4))
#plot(ooh,col='red',xlab = "Year, Month")

#par(mfrow=c(2,2))

tv<-ts(dataset2[,6],frequency = 12, start = c(2016,4))
#plot(tv,col='red',xlab = "Year, Month")

search<-ts(dataset2[,7],frequency = 12, start = c(2016,4))
#plot(search,col='red',xlab = "Year, Month")

display<-ts(dataset2[,8],frequency = 12, start = c(2016,4))
#plot(display,col='red',xlab = "Year, Month")

social<-ts(dataset2[,9],frequency = 12, start = c(2016,4))
#plot(social,col='red',xlab = "Year, Month")

#par(mfrow=c(1,1))
sales<-ts(dataset2[,13],frequency = 12, start = c(2016,4))
#plot(sales,col='blue',xlab = "Year, Month")

model_magazine<- arima(magazine,order=c(1,0,0))
model_magazine$coef
# 0.76562914 

model_newspaper<- arima(newspaper,order=c(1,0,0))
model_newspaper$coef
#0.0088094801

model_radio<- arima(radio,order=c(1,0,0))
model_radio$coef
#0.7708118

model_ooh<- arima(ooh,order=c(1,0,0))
model_ooh$coef
#0.0470632289

model_tv<- arima(tv,order=c(1,0,0))
model_tv$coef
# 0.57877294

model_search<- arima(search,order=c(1,0,0))
model_search$coef
#0.050634845

model_display<- arima(display,order=c(1,0,0))
model_display$coef
#0.117118041

model_social<- arima(social,order=c(1,0,0))
model_social$coef
#0.601925525




ad1.adstock <- function(x=dataset2[,2], rate=0.76){return(as.numeric(stats::filter(x=x, filter=rate, method="recursive")))}
ad2.adstock <- function(x=dataset2[,3], rate=0.008){return(as.numeric(stats::filter(x=x, filter=rate, method="recursive")))}
ad3.adstock <- function(x=dataset2[,4], rate=0.78){return(as.numeric(stats::filter(x=x, filter=rate, method="recursive")))}
ad4.adstock <- function(x=dataset2[,5], rate=0.05){return(as.numeric(stats::filter(x=x, filter=rate, method="recursive")))}
ad5.adstock <- function(x=dataset2[,6], rate=0.58){return(as.numeric(stats::filter(x=x, filter=rate, method="recursive")))}
ad6.adstock <- function(x=dataset2[,7], rate=0.051){return(as.numeric(stats::filter(x=x, filter=rate, method="recursive")))}
ad7.adstock <- function(x=dataset2[,8], rate=0.12){return(as.numeric(stats::filter(x=x, filter=rate, method="recursive")))}
ad8.adstock <- function(x=dataset2[,9], rate=0.60){return(as.numeric(stats::filter(x=x, filter=rate, method="recursive")))}


nrow(dataset2)
#trend = nrow(dataset2)
trend = 1:35
View(dataset2)

#ad1.adstock()

modFit.3 <- glm(dataset2[,13]~trend+ad1.adstock()+ad2.adstock()+ad3.adstock()+ad4.adstock()+ad5.adstock()+ad6.adstock()+ad7.adstock()+ad8.adstock() + dataset2$Price2 + dataset2$Price3)



summary(modFit.3)
plot(modFit.3)

anova(modFit.3)

mse_loocv <- cv.glm(dataset2,modFit.3)$delta[1]


mse_loocv

summary(mse_loocv)

modFit.3$coefficients
modFit.3$fitted.values
dataset2[,13]






adstock_rate <- 0.50
max_memory   <- 2
learn_rates <- rep(adstock_rate, max_memory+1) ^ c(0:max_memory)

ad1.adstock <- as.numeric(stats::filter(c(rep(0, max_memory), dataset2[,2]), learn_rates, method="convolution"))

ad1.adstock <- ad1.adstock[!is.na(ad1.adstock)]
# Graph Data
plot(seq(1,length(dataset2[,2])), dataset2[,2], type="h", 
     xlab="Time (in months)", ylab="Magazine", 
     ylim=c(0, max(c(dataset2[,2], ad1.adstock))), 
     frame.plot=FALSE)
lines(ad1.adstock)


ad2.adstock <- as.numeric(stats::filter(c(rep(0, max_memory), dataset2[,3]), learn_rates, method="convolution"))
ad2.adstock <- ad2.adstock[!is.na(ad2.adstock)]
# Graph Data
plot(seq(1,length(dataset2[,3])), dataset2[,3], type="h", 
     xlab="Time (in months)", ylab="Newspaper", 
     ylim=c(0, max(c(dataset2[,3], ad2.adstock))), 
     frame.plot=FALSE)
lines(ad2.adstock)


ad3.adstock <- as.numeric(stats::filter(c(rep(0, max_memory), dataset2[,4]), learn_rates, method="convolution"))
ad3.adstock <- ad3.adstock[!is.na(ad3.adstock)]
# Graph Data
plot(seq(1,length(dataset2[,4])), dataset2[,4], type="h", 
     xlab="Time (in months)", ylab="Radio", 
     ylim=c(0, max(c(dataset2[,4], ad3.adstock))), 
     frame.plot=FALSE)
lines(ad3.adstock)

ad4.adstock <- as.numeric(stats::filter(c(rep(0, max_memory), dataset2[,5]), learn_rates, method="convolution"))
ad4.adstock <- ad4.adstock[!is.na(ad4.adstock)]
# Graph Data
plot(seq(1,length(dataset2[,5])), dataset2[,5], type="h", 
     xlab="Time (in months)", ylab="OOH", 
     ylim=c(0, max(c(dataset2[,5], ad4.adstock))), 
     frame.plot=FALSE)
lines(ad4.adstock)


ad5.adstock <- as.numeric(stats::filter(c(rep(0, max_memory), dataset2[,6]), learn_rates, method="convolution"))
ad5.adstock <- ad5.adstock[!is.na(ad5.adstock)]
# Graph Data
plot(seq(1,length(dataset2[,6])), dataset2[,6], type="h", 
     xlab="Time (in months)", ylab="TV", 
     ylim=c(0, max(c(dataset2[,6], ad5.adstock))), 
     frame.plot=FALSE)
lines(ad5.adstock)

ad6.adstock <- as.numeric(stats::filter(c(rep(0, max_memory), dataset2[,7]), learn_rates, method="convolution"))
ad6.adstock <- ad6.adstock[!is.na(ad6.adstock)]
# Graph Data
plot(seq(1,length(dataset2[,7])), dataset2[,7], type="h", 
     xlab="Time (in months)", ylab="Search", 
     ylim=c(0, max(c(dataset2[,7], ad6.adstock))), 
     frame.plot=FALSE)
lines(ad6.adstock)

ad7.adstock <- as.numeric(stats::filter(c(rep(0, max_memory), dataset2[,8]), learn_rates, method="convolution"))
ad7.adstock <- ad7.adstock[!is.na(ad7.adstock)]
# Graph Data
plot(seq(1,length(dataset2[,8])), dataset2[,8], type="h", 
     xlab="Time (in months)", ylab="Display", 
     ylim=c(0, max(c(dataset2[,8], ad7.adstock))), 
     frame.plot=FALSE)
lines(ad7.adstock)

ad8.adstock <- as.numeric(stats::filter(c(rep(0, max_memory), dataset2[,9]), learn_rates, method="convolution"))
ad8.adstock <- ad8.adstock[!is.na(ad8.adstock)]
# Graph Data
plot(seq(1,length(dataset2[,9])), dataset2[,9], type="h", 
     xlab="Time (in months)", ylab="Social", 
     ylim=c(0, max(c(dataset2[,9], ad8.adstock))), 
     frame.plot=FALSE)
lines(ad8.adstock)



nrow(dataset2)
#trend = nrow(dataset2)
trend = 1:35
View(dataset2)


library(DAAG)
#library(rlang)

#train_control <- trainControl(method="cv", number=10,verboseIter = TRUE)
modFit.3 <- cv.lm(dataset2[,13]~trend+ad1.adstock+ad2.adstock+ad3.adstock+ad4.adstock+ad5.adstock+ad6.adstock+ad7.adstock+ad8.adstock + dataset2$Price2 + dataset2$Price3,m=10,plotit=F)



summary(modFit.3)
#plot(modFit.3)

#anova(modFit.3)

#mse_loocv <- cv.glm(dataset2,modFit.3)$delta[1]


#mse_loocv

#summary(mse_loocv)

modFit.3$coefficients
modFit.3$fitted.values

# Graph Data
plot(seq(1,length(dataset2[,13])), dataset2[,13], type="h", 
     xlab="Time (in months)", ylab="Sales", 
     ylim=c(0, max(c(dataset2[,13], modFit.3$fitted.values))), 
     frame.plot=FALSE)
lines(modFit.3$fitted.values)







